\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,booktabs}
\usepackage[hidelinks]{hyperref}

\title{Supplementary Material:\\
Deployment Calibration Trace for\\
\emph{The Price of Fairness, Complexity, and Incentives in
No-Numeraire Combinatorial Trade-Intent Auctions}}
\author{}
\date{}

\begin{document}
\setlength{\emergencystretch}{3em}
\maketitle

\noindent
This anonymized supplement provides the deployment summary statistics used
in Section~7 of the submission, so that the reported figures can be
verified without de-anonymizing the authors. The underlying per-auction
records and the reproduction scripts are included in the accompanying
archive. We reiterate the scope stated in the main text: these are
\textbf{observable deployment diagnostics, not estimates of the structural
complementarity factor $g$}. The trace records winner and runner-up
solution scores and order-level notionals, but not the full vector of
per-leg standalone valuations required to compute $V(S)/\sum_j V(\{j\})$;
the worst-case results of the submission hold for any $g$.

\section*{S1. Trace scale}

\begin{table}[h]
\centering
\begin{tabular}{@{}lr@{}}
\toprule
Quantity & Value \\
\midrule
Post-adoption solver competitions & $802{,}816$ \\
Observation window & 8 months \\
Covered notional & \$54.69\,B \\
Visible accounting gap (aggregate) & \$5.13\,M \\
Visible accounting gap (relative) & $\approx 0.94$ bps \\
\bottomrule
\end{tabular}
\caption{Scale of the deployment trace. The visible accounting gap is the
aggregate difference between the winning solution's score and the best
non-winning visible score on the sane-volume USD subsample.}
\end{table}

\section*{S2. Visible coverage / spread distribution}

For each auction, let $\mathrm{Score}_1$ be the winning solution's score
and $\mathrm{Score}^{\mathrm{other}}_2$ the best positive score submitted
by a different solver. Define the observable
\[
\widehat\alpha^{\mathrm{obs}}
=\frac{\mathrm{Score}^{\mathrm{other}}_2}{\mathrm{Score}_1}\in[0,1],
\qquad
\widehat G^{\mathrm{obs}}=1/\widehat\alpha^{\mathrm{obs}}\ge1 ,
\]
with $\widehat G^{\mathrm{obs}}=\infty$ when
$\widehat\alpha^{\mathrm{obs}}=0$.
This is an \emph{auction-level} visible coverage; it is a proxy for, and
weaker than, the per-leg coverage parameter of the submission's
coverage law, which would require per-leg standalone benchmarks.

\begin{table}[h]
\centering
\begin{tabular}{@{}lr@{}}
\toprule
Event & Share of auctions \\
\midrule
Visible spread $\widehat G^{\mathrm{obs}}>2$ (all orders) & $25.3\%$ \\
Visible spread $\widehat G^{\mathrm{obs}}>4$ (all orders) & $20.2\%$ \\
Visible spread $\widehat G^{\mathrm{obs}}>2$ (small-notional orders) & $63.1\%$ \\
\bottomrule
\end{tabular}
\caption{Tail of the visible-spread distribution. A non-trivial spread is
the common case rather than a corner, especially for small orders.}
\end{table}

\section*{S3. Benchmark robustness}

Under a naive local hard-reserve benchmark (reserve computed from a short
local window with no inheritance or smoothing), we replay a single
low-quote injection per cell-window and record whether it would move the
published benchmark enough to admit an otherwise-filtered settlement.

\begin{table}[h]
\centering
\begin{tabular}{@{}lr@{}}
\toprule
Benchmark variant & Vulnerable cell-windows (auction-weighted) \\
\midrule
Local hard reserve (naive) & $97.1\%$ \\
\bottomrule
\end{tabular}
\caption{Fragility of a naive benchmark to single-injection contamination,
motivating the delayed / quantile / rate-limited / parent-cell-inherited
benchmarks analyzed in the submission's contamination game. The replay
parameters and robust-reserve configuration are in the accompanying
scripts.}
\end{table}

\section*{S4. Reproducibility note}

All figures below are computed from an anonymized deployment trace of
post-CIP-67 solver competitions. Identifying metadata is removed, and the
computation scripts are included in the accompanying anonymized archive.

\paragraph{Sample.}
The main sample contains 802,816 mainnet solver competitions from June 1,
2025 through January 31, 2026. The parser retains protocol-valid,
non-filtered, positive-score solver submissions. Full-sample quantities
such as visible spread and effective solver count use all parsed auctions.
USD-denominated quantities use smaller denominators: 680,839
score-to-USD observations, 493,653 notional-covered observations, and
318,469 sane-volume observations with $\mathrm{volume\_usd}\in[1,10^7]$.
These denominator changes are intentional coverage restrictions, not
inconsistencies.

\paragraph{Score variables.}
For each competition, $\mathrm{Score}_1$ is the winning solution score.
The reference score $\mathrm{Score}^{\mathrm{other}}_2$ is the best
positive score submitted by a solver different from the winner. The
parser groups by solver identity, removes all candidate solutions
submitted by the winning solver, and then takes the maximum remaining
positive valid score; if none exists, the reference score is zero. This
best-non-winning-solver construction differs from a raw second-solution
parser on 11.8\% of auctions, and 15.2\% of retained auctions have no
positive non-winning solver score.

\paragraph{Visible spread.}
The visible spread is
\[
\widehat G^{\mathrm{obs}}
=\frac{\mathrm{Score}_1}{\mathrm{Score}^{\mathrm{other}}_2},
\]
with infinite spread when the best non-winning solver score is zero. The
reported tail shares are computed on the full 802,816-auction sample:
$\widehat G^{\mathrm{obs}}>2$ in 25.3\% of auctions and
$\widehat G^{\mathrm{obs}}>4$ in 20.2\%. The small-notional segment is
the bottom size bucket produced by the score-winner quantile rule
$(0,0.25,0.75,0.90,1.0)$; it contains 200,704 auctions and has
$\widehat G^{\mathrm{obs}}>2$ in 63.1\%.

\paragraph{Accounting gap.}
The score difference is converted to dollars using ETH/USD prices:
\[
\mathrm{ScoreDiffUSD}
=\frac{\mathrm{Score}_1-\mathrm{Score}^{\mathrm{other}}_2}{10^{18}}
\cdot \mathrm{ETHUSD}.
\]
The reported \$5.13M aggregate winsorizes this dollar gap at the first
and ninety-ninth percentiles and sums over the sane-volume denominator
above. The \$54.69B covered notional is the sell-token notional over the
same denominator, and the 0.94 bps figure is
$10^4$ times aggregate gap divided by covered notional.

\paragraph{Reserve-vulnerability diagnostic.}
The benchmark diagnostic uses cell-windows from the reserve-construction
pipeline. With baseline quantile $\tau=0.25$, a cell-window is marked
vulnerable if the maximum eligible-sample share of any single solver is
at least $\tau$, meaning that a single solver could potentially influence
the local reserve quantile if its samples were contaminated. The
diagnostic contains 91,390 cell-windows; 99.6\% are vulnerable
unweighted, and 97.1\% are vulnerable after auction-weighting. The
corresponding design implication is to inherit from parent cells or use
audit-only/soft reserves when local support is sparse.

\paragraph{Scripts.}
The archive includes the parser and metric construction scripts
\texttt{build\_dataset.py}, \texttt{add\_usd\_prices.py}, and
\texttt{fragility.py}; validation scripts including
\texttt{sample\_flow.py}, \texttt{usd\_missingness.py},
\texttt{reference\_score\_validation.py}, and the reserve-vulnerability
diagnostic; and table-generation scripts producing the summary CSV and
\LaTeX{} tables. Large per-auction parquet files are represented in the
submission archive by anonymized processed records or deterministic CSV
summaries, depending on upload-size constraints.

\end{document}
